\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-15 report/paper.tex
started on implementation

\section{Implementation}
%Details of how it was done
%What hardware
%What software
%Why did you do it that way?
%What limitations, if any, did this present?
%*No code*!!!!!

    % Talk about what we used for plugins, computers etc maybe or should this be in method?

@@

@@

>>>>

\section{Implementation}
%Details of how it was done
%What hardware
%What software
%Why did you do it that way?
%What limitations, if any, did this present?
%*No code*!!!!!
    % Talk about what we used for plugins, computers etc maybe or should this be in method?

    % Libraries
    % Computers
    % OpenGL
    % language
    % Makefiles
    The divergence-free SPH simulation was developed using OpenGL and C++ together with the OpenGL mathematics library GLM for vector calculations.
    FreeImage was used to save frames of the simulation and FFmpeg to assembled the frames into a video.
    PicoJSON was used to load in variables from a file making it easier to change variables quick and efficient and a makefile was used to compile the project.

    The simulation was developed on Mac OS and Linux.
    The Linux computer is running on Debian and has four Intel(R) Core(TM) i5-2450M CPU @ 2.50GHz, one NVIDIA GeForce 610M graphics card and 6.0 GiB RAM.

@@

    % Write about FPS when running x amount of particles

@@

% Parallelize
